Computational Prediction of Boundaries of 3D Genomic Domains in Class Imbalance

### 2019-05-09 Manuscript/manuscript.Rmd
editted manuscript and added to to do

Biological replicate Hi-C data for the GM12878 and K562 cell lines were downloaded from GEO GSE63525 [@rao20143d] (Supplementary Table 1). The autosomal genomic coordinates (GRCh37/hg19 human genome assembly) of TAD boundaries were obtained from data at 10 kb, 25 kb, 50 kb, and 100 kb resolution using the Arrowhead algorithm [@durand2016juicebox]. <!--For each of the 4 data resolutions, a total of 8008, 4869, 2449, and 1075 unique TADs were extracted from the GM12878 cell line, and a total of 5828, 4097, 2181, and 986 unique TADs were extracted from the K562 cell line. The TADs were distributed throughput the autosomal chromosomes, with larger chromosomes containing more TADs (Supplementary Figure 14; Supplementary Table 8).--> The start and end coordinates of all TADs were concatenated, sorted, and unique TAD boundary points were obtained throughput the autosomal chromosomes. TAD boundaries called on Chromosome 9 were omitted from all downstream analyses, for both cell lines, due to the sparcity of the contact matrix at the 10 kb resolution for the K562 cell line.

>>>>

Biological replicate Hi-C data for the GM12878 and K562 cell lines were downloaded from GEO GSE63525 [@rao20143d] (Supplementary Table 1). The autosomal genomic coordinates (GRCh37/hg19 human genome assembly) of TAD boundaries were obtained from data at 10 kb, 25 kb, 50 kb, and 100 kb resolution using the Arrowhead algorithm [@durand2016juicebox]. The start and end coordinates of all TADs were concatenated, sorted, and unique TAD boundary points were obtained throughput the autosomal chromosomes. TAD boundaries called on Chromosome 9 were omitted from all downstream analyses, for both cell lines, due to the sparcity of the contact matrix at the 10 kb resolution for the K562 cell line.
